Robotic models of learning and development \\of speech and tool use.

### 2015-10-08 roadmap/doc.tex
different hierarchies
experiments

	\subsection{Motivation}

@@

@@

@@

			\paragraph{}
			Abstract environment with forward models defined by mathematical functions. 
			It should be interesting to use some sort of benchmark to control the complexity of functions.

			\paragraph{}
			Different variables to test:
			\begin{itemize}
				\item Motor and Sensory dimensionalities,
				\item Complexity of hierarchies (with a measure of it),
				\item Perturbations of forward models at different hierarchy levels.
			\end{itemize}

@@

		\subsubsection{Measures}

>>>>

	\subsection{Introduction}

@@

	\subsection{Questions}

		\begin{itemize}
			\item Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.
			\item Which task should I explore now ?
			\item How to choose between different means to explore a given space ? 
			\item How can high-level tasks guide the exploration of lower-level ones ?
			\item How can the system cope with perturbations on some of the forward models ?		
		\end{itemize}

@@

		\subsubsection{Hierarchies}

			\begin{figure}[H] 
				\subfloat[]{\input{include/H1.tikz}}
				\subfloat[]{\input{include/H2.tikz}}
				\subfloat[]{\input{include/H3.tikz}}
				\subfloat[]{\input{include/H4.tikz}}
				\caption{Exemple of hierarchies.}
				\label{H}					
			\end{figure}
		%

@@

			\paragraph{}
			Different variables to test:
			\begin{itemize}
				\item Motor and Sensory dimensionalities,
				\item Type of functions: linear, cosine, geometric arm, non-continuous interaction with objects.
				\item Noise
			\end{itemize}

@@

		\subsubsection{Experiments}

				\paragraph{Experiment 1: Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.}
				\paragraph{}
				The idea is to compare our simplest algorithm (explore the module with higher progress) in a realistic setting (Hierarchy (a) of Fig. \ref{H}) to the control condition where a sensorimotor model is learned
				directly from the whole motor space $M$ to the whole sensori space $S$.

				\paragraph{Experiment 2: Which task should I explore now ?}
				\paragraph{}
				Here we compare the different possibilities to choose the module to explore in the hierarchy: maximizing the progress, maximizing with a bias towards lower-level modules, or use ZPDES,
				with the same hierarchy (a) of Fig. \ref{H}.

				\paragraph{Experiment 3: How to choose between different means to explore a given space ?}
				\paragraph{}
				Here we explain that we can choose between different means (e.g. different tools) using the one with the maximal competence.
				We can use the hierarchy (b) of Fig. \ref{H}.

				\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}
				\paragraph{}
				We compare different possibilities of Top-Down Guidance, 
				with hierarchy (c) of Fig. \ref{H}.

				\paragraph{Experiment 5: How can the system cope with perturbations on some of the forward models ?}
				\paragraph{}
				We apply perturbations to one of the possible forward models, either blocking, shifting or randomizing one dimension. 
				We can use the hierarchy (d) of Fig. \ref{H}.

		%
		\subsubsection{Measures}
